From textual to structured Web API Descriptions {\large Knowledge Discovery and Data Mining Seminar 2017}

### 2017-08-31 Paper/Paper_KDD.tex
Update references and url

\usepackage{scrextend}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{color}
\usepackage{amssymb}
\usepackage{varwidth}
\usepackage{setspace}

@@

\begin{abstract}
In this study, we investigate the possibility of using Knowledge Discovery and Data Mining approaches to transform human written textual Web Application Programming Interface
(API) descriptions into structural descriptions, which
can be consumed by machines. The central vision
is to provide a solution, which ultimately allows
machines to interchange APIs with similar purposes
automatically. A use case would be to replace non-
responding data providing API (e.g. weather,
location, news) with another. Using descriptions
provided by ProgrammableWeb, with over 15000
APIs one of the most prominent public API library,
we conducted multiple steps of data cleaning and
preprocessing followed by machine learning
algorithms (K-Means, DBSCAN) to create clusters,
which we validated manually. With an average of only
68,3 words per descriptions (45,6 after
preprocessing), we found that the amount of clusters are between 300 and 700 unique clusters. After social-tagging activities on the prototype-website\footnote{http://webapi.bplaced.net/} for about 300 APIs, we receive a quality score of 60~\%, which means, that more than half of the APIs are probably clustered correctly. But our results suggests, that the
needed quantity for text mining and clustering was insufficiently met. Our clusters were thus also inconclusive. 
The complete code is available on github\footnote{https://github.com/Cuky88/APICrawler}.
\end{abstract}

@@

\section{Datasets and Crawling}
%rechtsbündige grafik (habe ich jetzt erst mal rausgenommen, da es komisch aussah):
%\piccaption{Amount of working links in Programmable Web} 
%\parpic[r]{\includegraphics[width=1.5in]{img/pie.png}} 
Prior to our research and development, we looked for suitable datasets with good quality. There was not much research done in this field, therefore we had to look for different alternatives, which will be described in the following sections. Section II.A describes the Linked Web API dataset and its issues. Section II.B deals with the dataset crawled from Programmable Web  \footnote[1]{https://www.programmableweb.com} and section II.C shows an alternative way to get data from Google.

@@

\subsection{Programmable Web Dataset}
Another approach to get usable data was to crawl Programmable Web with over 15.800 APIs. Therefore, we constructed a crawler with the Scrapy Framework \footnote[2]{https://scrapy.org} to crawl all the data. The API descriptions from Programmable Web have an averege length of about 70 words, which we assumed to be not enough. We examined the links to the API documentation sites, to see if we can crawl them, too. From the 15.800 APIs, about 32~\% (Fig.  \ref{fig_sim3}) were not working. When we investigated the links deeper, we found out, that approximately 30 to 45~\% of the links redirect to a subpages like  main, authentication or payment pages. This was the same issue like with the Linked Web API dataset.
\begin{figure}[h]
\centering
\includegraphics[width= 3.5in]{img/graph1.pdf}
\caption{Amount of working links in Programmable Web}
\label{fig_sim3}
\end{figure}

@@

\subsection{Normalized Google Distance}
For the correlation matrix we tried to implement the algorithm introduced by Jian Wu, Liang Chen, Zibin Zheng, Michael R. Lyu and Zhaohui Wu in their Paper “Clustering Web services to facilitate service discovery” \cite{kanungo2002efficient}. The algorithm determines the similarity of each APIs word-vector with all the other word vectors by comparing the word in the word-vector with the normalized google distance. As a result, the algorithm produces a correlation-matrix where for any given API the distance to each other API can be withdrawn (Algorithm \ref{alg:algo1}).

@@

\subsection{Manual Evaluation}
We created a simple website\footnote{http://webapi.bplaced.net} to do social-tagging. It enables an easy manual evaluation and access to anyone to use our results. The data the site is based on is a JSON file. It contains the result of the K-Means clustering with a parameter combination that had one of the best quality measures.

@@

We prepared a github-wiki\footnote{https://github.com/Cuky88/APICrawler/wiki} with every needed information and a guide, how to setup and run the code.

>>>>

\usepackage{scrextend}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{color}
\usepackage{amssymb}
\usepackage{varwidth}
\usepackage{setspace}
\usepackage{url}
\def\UrlBreaks{\do\/\do.}
\usepackage{breakurl}
\usepackage[breaklinks]{hyperref}

@@

\begin{abstract}
In this study, we investigate the possibility of using Knowledge Discovery and Data Mining approaches to transform human written textual Web Application Programming Interface
(API) descriptions into structural descriptions, which
can be consumed by machines. The central vision
is to provide a solution, which ultimately allows
machines to interchange APIs with similar purposes
automatically. A use case would be to replace non-
responding data providing API (e.g. weather,
location, news) with another. Using descriptions
provided by ProgrammableWeb, with over 15000
APIs one of the most prominent public API library,
we conducted multiple steps of data cleaning and
preprocessing followed by machine learning
algorithms (K-Means, DBSCAN) to create clusters,
which we validated manually. With an average of only
68,3 words per descriptions (45,6 after
preprocessing), we found that the amount of clusters are between 300 and 700 unique clusters. After social-tagging activities on the prototype-website\footnote{\url{http://webapi.bplaced.net/}} for about 300 APIs, we receive a quality score of 60~\%, which means, that more than half of the APIs are probably clustered correctly. But our results suggests, that the
needed quantity for text mining and clustering was insufficiently met. Our clusters were thus also inconclusive. 
The complete code is available on github\footnote{\url{https://github.com/Cuky88/APICrawler}}.
\end{abstract}

@@

\section{Datasets and Crawling}
%rechtsbündige grafik (habe ich jetzt erst mal rausgenommen, da es komisch aussah):
%\piccaption{Amount of working links in Programmable Web} 
%\parpic[r]{\includegraphics[width=1.5in]{img/pie.png}} 
Prior to our research and development, we looked for suitable datasets with good quality. There was not much research done in this field, therefore we had to look for different alternatives, which will be described in the following sections. Section II.A describes the Linked Web API dataset and its issues. Section II.B deals with the dataset crawled from Programmable Web  \footnote[1]{\url{https://www.programmableweb.com}} and section II.C shows an alternative way to get data from Google.

@@

\subsection{Programmable Web Dataset}
Another approach to get usable data was to crawl Programmable Web with over 15.800 APIs. Therefore, we constructed a crawler with the Scrapy Framework \footnote[2]{\url{https://scrapy.org}} to crawl all the data. The API descriptions from Programmable Web have an averege length of about 70 words, which we assumed to be not enough. We examined the links to the API documentation sites, to see if we can crawl them, too. From the 15.800 APIs, about 32~\% (Fig.  \ref{fig_sim3}) were not working. When we investigated the links deeper, we found out, that approximately 30 to 45~\% of the links redirect to a subpages like  main, authentication or payment pages. This was the same issue like with the Linked Web API dataset.
\begin{figure}[h]
\centering
\includegraphics[width= 3.5in]{img/graph1.pdf}
\caption{Amount of working links in Programmable Web}
\label{fig_sim3}
\end{figure}

@@

\subsection{Normalized Google Distance}
For the correlation matrix we tried to implement the algorithm introduced by J. Wu, L. Chen, Z. Zheng, M. R. Lyu and Z. Wu in their Paper “Clustering Web services to facilitate service discovery” \cite{wu2014}. The algorithm determines the similarity of each APIs word-vector with all the other word vectors by comparing the word in the word-vector with the normalized google distance. As a result, the algorithm produces a correlation-matrix where for any given API the distance to each other API can be withdrawn (Algorithm \ref{alg:algo1}).

@@

\subsection{Manual Evaluation}
We created a simple website\footnote{\url{http://webapi.bplaced.net}} to do social-tagging. It enables an easy manual evaluation and access to anyone to use our results. The data the site is based on is a JSON file. It contains the result of the K-Means clustering with a parameter combination that had one of the best quality measures.

@@

We prepared a github-wiki\footnote{\url{https://github.com/Cuky88/APICrawler/wiki}} with every needed information and a guide, how to setup and run the code.
